### 2022-01-26 input/abstract.tex
small rewording to avoid downloaded repetition

  %% \NAME is a crazy contribution
  \color{red} \NAME can constitute a novel building block for
  geo-distributed services, \eg sharing the locations of downloaded
  web objects to allow nodes benefit from neighborhood downloads,
  resource discovery in the vicinity of a region, etc.

>>>>

  %% \NAME is a crazy contribution
  \color{red} \NAME can constitute a novel building block for
  geo-distributed services, \eg sharing the locations of 
  web object replicas to allow nodes benefit from neighborhood downloads,
  resource discovery in the vicinity of a region, etc.
